### 2017-01-02 Plos-one-manuscript/latex/manuscript.tex
added SI and updated figures

Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
At larger volumes this effect is more pronounced resulting in the volume measured being greater then the amount of liquid pulled into the syringe.
We remedied this by creating a new scale to account for the expansion.
The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements. 
\subsection*{Fabrication \& Assembly}
Two parts are printed (body.stl and plunger.stl) at normal resolution with rafts on a Makerbot Replicator.
A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
The nut is sunk in to the hex inset in the printed body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 uL configuration.
Springs are placed inside a 3 mL syringe for the 100-1000 mL configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly(fig.~\ref{fig3}).
Parts and cost are listed in Table~\ref{table1} and \ref{table2}.

@@

\begin{figure}
\caption{
{\bf Photos of pipette.}  The pipette is composed of two printed parts, a 1 mL syringe and some additional hardware.  
}
\label{fig3}
\end{figure}

>>>>

Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
At larger volumes this effect is more pronounced resulting in the volume measured being greater then the amount of liquid pulled into the syringe.
We remedied this by creating a new scale to account for the expansion.
The scale is printed on a transparency sheet and is taped onto the syringe for accurate measurements (See~\nameref{S1_Fig} and \nameref{S2_Fig}).

\subsection*{Fabrication \& Assembly}
Two parts are printed (body.stl and plunger.stl) at normal resolution with rafts on a Makerbot Replicator.
A small amount of paraffin wax is applied to the screw to prevent slop from causing the set point to drift after each actuation.
The nut is sunk in to the hex inset in the printed body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of a 1 mL syringe for the 30-300 uL configuration.
Springs are placed inside a 3 mL syringe for the 100-1000 mL configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly(fig.~\ref{fig3}).
Parts and cost are listed in Table~\ref{table1} and \ref{table2}.

\begin{figure}
	\caption{
		{\bf Photos of assembled pipettes.}  (A) Two assemblies of the pipette: the 100-1000 uL configuration (above) and the 30-300 uL configuration (below). (B) Close-up photo of the taped on scale for each of the syringes. 
	}
	\label{fig3}
\end{figure}

@@
